---
title: "Real-world simulated data(RWSD) scRNAseq datasets and gene signature simulation"
output: 
  html_notebook: 
    code_folding: hide
    theme: readable
editor_options: 
  chunk_output_type: console
---

```{r set-up, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE, autodep=TRUE, message=FALSE, warning=FALSE)
library(Seurat)
rm(list=ls())
gc()
```

```{r scimpute data}
File_dir = "/gpfs/fs2/scratch/rwang46/Single Cell Pathway Score_scPS/Job 1 Simulation/Script/"
setwd(File_dir)
Normal_Bcell.data <- read.csv("./Scenario 2 scimpute count data/scimpute_count.csv",header = T, row.names = 1)
Normal_Bcell <- CreateSeuratObject(counts = Normal_Bcell.data, project = "scimpute", min.cells = 3, min.features = 200)
Normal_Bcell <- NormalizeData(Normal_Bcell, normalization.method = "LogNormalize", scale.factor = 10000)
save(Normal_Bcell,file = "Naive Normal B cell_scimpute.RData")
load("/gpfs/fs2/scratch/rwang46/Single Cell Pathway Score_scPS/Job 1 Simulation/Script/Naive Normal B cell_scimpute.RData")
```

```{r real-world simulated data (RWSD), cellcount, threshold, signal level}
load("/gpfs/fs2/scratch/rwang46/Single Cell Pathway Score_scPS/Job 1 Simulation/Script/Naive Normal B cell.RData")
DefaultAssay(Normal_Bcell) <- "RNA"
# DimPlot(Normal_Bcell, reduction = "pca")
# Idents(Normal_Bcell) <- "annotation"
# table(Idents(Normal_Bcell))
# Idents(Normal_Bcell) <- "Group"
# table(Idents(Normal_Bcell))
# save(Normal_Bcell,file = "./Naive Normal B cell.RData")
```


```{r file}
File_dir = "/gpfs/fs2/scratch/rwang46/Single Cell Pathway Score_scPS/Job 1 Simulation/Practical/Sample size 200"
dir.create(File_dir)
# set the parameters
cellcounts = 200 #sample size for each condition
Threshold = 0.75
Signal_Level = 1.2
set.seed(42)
sim.mc <- replicate(11, {X <- sample(1:length(colnames(Normal_Bcell)),(2*cellcounts),replace=F)})
```

Scenario 1: 
Remove undetected genes
Select Densely expressed genes, and ddd signal to these genes in condition 2
Signal is 100% from densely expressed genes,and Non-signal is from the remaining genes
GS size 10-500 and Sample size 20,50,200,500
```{r RWSD Scenario 1}
setwd(File_dir)
File_dir
#Scenario_set = "Scenario 1 without signal"
Scenario_set = "Scenario 1 scimpute"
dir.create(Scenario_set)
file_dir = paste0(File_dir,"/",Scenario_set)
Genes <- list()
Signal <- list()
NonSignal <- list()
Undetect <- list()
rows_zeros.signal <- list()
rows_zeros.nonsignal <- list()
p_DimPlot<-list()

for (repl in 1:10){
  B_cell_subset <- Normal_Bcell[,colnames(Normal_Bcell)[sim.mc[,repl]]]
  rownames(B_cell_subset@assays$RNA@data) <- paste0("gene",rep(1:dim(B_cell_subset)[1]))
  B_cell_subset_meta_data <- data.frame(Condition=c(rep("Condition_1",cellcounts),rep("Condition_2",cellcounts))) # add condition meta
  set.seed(42)
  condition_1 <-sample(colnames(B_cell_subset),cellcounts,replace = F)
  condition_2 <- setdiff(rownames(B_cell_subset@meta.data),condition_1)
  rownames(B_cell_subset_meta_data) <- c(condition_1,condition_2)
  B_cell_subset <- AddMetaData(B_cell_subset,metadata = B_cell_subset_meta_data)
  Idents(B_cell_subset) <- 'Condition'
  print(table(Idents(B_cell_subset)))
  #p <- DimPlot(B_cell_subset, reduction = "pca")
  
  ## ----Gene signature simulation--------------------------------------------------
  rows_zeros = rowMeans(B_cell_subset@assays$RNA@data ==0)
  # Scenario 1 select genes detected in at least one cell
  Genes[[repl]] <- rownames(B_cell_subset@assays$RNA@data[rows_zeros < 1,])
  print(paste("Detected gene count",length(Genes[[repl]])))
  Undetect[[repl]] <- rownames(B_cell_subset@assays$RNA@data[rows_zeros == 1,])
  print(paste("Undetect gene count",length(Undetect[[repl]])))

  # Assign signal
  Signal[[repl]] <- rownames(B_cell_subset@assays$RNA@data[rows_zeros < Threshold,])
  print(paste("Signal gene count",length(Signal[[repl]])))
  NonSignal[[repl]] <- Genes[[repl]][-which(Genes[[repl]] %in% Signal[[repl]]) ]
  print(paste("Non singal gene count",length(NonSignal[[repl]])))
  
  dat <- as.matrix(B_cell_subset@assays$RNA@data)
  dat <- dat[rownames(dat) %in% Genes[[repl]],]
  print(dim(dat))
  dat[Signal[[repl]], which(B_cell_subset@meta.data$Condition %in% "Condition_2")] <- dat[Signal[[repl]], which(B_cell_subset@meta.data$Condition %in% "Condition_2")] * Signal_Level

  # Create Seurat Object
  Participant.integrated.1 <- CreateSeuratObject(counts = dat, project = "Scenario 2")
  rows_zeros = rowMeans(Participant.integrated.1@assays$RNA@counts ==0)
  names(rows_zeros) <- rownames(Participant.integrated.1)
  rows_zeros.signal[[repl]] <- rows_zeros[Signal[[repl]]]
  rows_zeros.nonsignal[[repl]] <- rows_zeros[NonSignal[[repl]]]
  
  Participant.integrated.1 <- ScaleData(Participant.integrated.1,verbose = F)
  # Add condition meta
  Participant.integrated.1 <- AddMetaData(Participant.integrated.1,metadata = B_cell_subset@meta.data$Condition ,col.name = 'Condition')
  Idents(Participant.integrated.1) <- 'Condition'
  table(Idents(Participant.integrated.1))
  save(Participant.integrated.1,file = paste(file_dir,"/rep",repl," sim.RData",sep = ""))

  # # Identify the 10 most highly variable genes
  # top10 <- head(VariableFeatures(Participant.integrated.1), 10)
  # # plot variable features with and without labels
  # plot1 <- VariableFeaturePlot(Participant.integrated.1)
  # plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
  # plot1 + plot2
  
  # Participant.integrated.1 <- FindVariableFeatures(Participant.integrated.1, selection.method = "vst", nfeatures = 2000)
  # Participant.integrated.1 <- RunPCA(Participant.integrated.1, features = VariableFeatures(object = Participant.integrated.1))
  # Participant.integrated.1 <- RunPCA(Participant.integrated.1, features = Signal[[repl]], verbose = F)
  # p_DimPlot[[repl]] <- DimPlot(Participant.integrated.1, reduction = "pca",label.size = 1)
  
  # gene set size from 10 to 500
  noise <- c(0,0.2,0.5,0.8,1)
  GS_size <- c(10,20,30,40,50,100,200,300,400,500)
  up_sim<- list()
  for (i in 1:length(noise)){
    up_sim[[i]] <- paste("GS",c(rep(GS_size,each=100)),noise[i],1:100,sep = "_")
  }
  # create the gold-stander genesets
  gs<- list()
  set.seed(42)
  for (i in 1:10){
    N= GS_size[i]
    for (sim in 1:100){
      if (length(Signal[[repl]]) >= N){
        gs[[up_sim[[1]][sim+100*(i-1)]]] <- c(sample(Signal[[repl]],size = N,replace = F))
      } else{
        gs[[up_sim[[1]][sim+100*(i-1)]]] <- 0
      }
    }
  }
  # create genesets with noise
  set.seed(42)
  for (i in 2:length(noise)){
    for (j in 1:10){
      N= GS_size[j]
      for (sim in 1:100){
        if (length(Signal[[repl]]) >= (N-N*noise[i])){
          gs[[up_sim[[i]][sim+100*(j-1)]]] <- c(sample(Signal[[repl]],size = N*round((1-noise[i]),1),replace = F),sample(NonSignal[[repl]],size = N*noise[i],replace = F))
        }
        else{
          gs[[up_sim[[i]][sim+100*(j-1)]]] <- 0
        }
      }
    }
  }
  # make geneset.gmt file
  file = paste(file_dir,"/rep",repl," GS.gmt",sep = "")
  write.gmt <- function(gs,file){
    sink(file)
    lapply(names(gs),function(i){
      cat(paste(c(i,'tmp',gs[[i]]),collapse = '\t'))
      cat('\n')
    })
    sink()
  }
  write.gmt(gs,file)
}

# save
saveRDS(rows_zeros.signal,file = "Scenario1_rows_zeros.signal.RWSD.rds")
saveRDS(rows_zeros.nonsignal,file = "Scenario1_rows_zeros.nonsignal.RWSD.rds")
```

Scenario 2: 
Remove undetected genes
Randomly select 550 genes, and ddd signal to these genes in condition 2
Signal is 100% from the selected genes, and Non-signal is from the remaining genes
GS size 10-500, and Sample size 20,50,200,500
```{r RWSD Scenario 2}
setwd(File_dir)
File_dir
#Scenario_set = "Scenario 2 without signal"
Scenario_set = "Scenario 2 scimpute"
dir.create(Scenario_set)
file_dir = paste0(File_dir,"/",Scenario_set)
Genes <- list()
Signal <- list()
NonSignal <- list()
Undetect <- list()
rows_zeros.signal <- list()
rows_zeros.nonsignal <- list()
p_DimPlot<-list()

for (repl in 1:10){
  B_cell_subset <- Normal_Bcell[,colnames(Normal_Bcell)[sim.mc[,repl]]]
  rownames(B_cell_subset@assays$RNA@data) <- paste0("gene",rep(1:dim(B_cell_subset)[1]))
  B_cell_subset_meta_data <- data.frame(Condition=c(rep("Condition_1",cellcounts),rep("Condition_2",cellcounts))) # add condition meta
  set.seed(42)
  condition_1 <-sample(colnames(B_cell_subset),cellcounts,replace = F)
  condition_2 <- setdiff(rownames(B_cell_subset@meta.data),condition_1)
  rownames(B_cell_subset_meta_data) <- c(condition_1,condition_2)
  B_cell_subset <- AddMetaData(B_cell_subset,metadata = B_cell_subset_meta_data)
  Idents(B_cell_subset) <- 'Condition'
  print(table(Idents(B_cell_subset)))
  
  ## ----Gene signature simulation--------------------------------------------------
  rows_zeros = rowMeans(B_cell_subset@assays$RNA@data ==0)
  # Scenario 1 select genes detected in at least one cell
  Genes[[repl]] <- rownames(B_cell_subset@assays$RNA@data[rows_zeros < 1,])
  print(paste("Detected gene count",length(Genes[[repl]])))
  Undetect[[repl]] <- rownames(B_cell_subset@assays$RNA@data[rows_zeros == 1,])
  print(paste("Undetect gene count",length(Undetect[[repl]])))
  
  # Assign signal
  set.seed(42)
  Signal[[repl]] <- sample(rownames(B_cell_subset@assays$RNA@data[rows_zeros < 1,]),550)
  print(paste("Signal genes counts",length(Signal[[repl]])))
  NonSignal[[repl]] <- Genes[[repl]][-which(Genes[[repl]] %in% Signal[[repl]]) ]
  print(paste("Non singal gene count",length(NonSignal[[repl]])))
  dat <- as.matrix(B_cell_subset@assays$RNA@data)
  dat <- dat[rownames(dat) %in% Genes[[repl]],]
  print(dim(dat))
  dat[Signal[[repl]], which(B_cell_subset@meta.data$Condition %in% "Condition_2")] <- dat[Signal[[repl]], which(B_cell_subset@meta.data$Condition %in% "Condition_2")] * Signal_Level

  # Create Seurat Object
  Participant.integrated.1 <- CreateSeuratObject(counts = dat, project = "Scenario 2")
  rows_zeros = rowMeans(Participant.integrated.1@assays$RNA@counts ==0)
  names(rows_zeros) <- rownames(Participant.integrated.1)
  rows_zeros.signal[[repl]] <- rows_zeros[Signal[[repl]]]
  rows_zeros.nonsignal[[repl]] <- rows_zeros[NonSignal[[repl]]]
  
  Participant.integrated.1 <- ScaleData(Participant.integrated.1,verbose = F)
  # Add condition meta
  Participant.integrated.1 <- AddMetaData(Participant.integrated.1,metadata = B_cell_subset@meta.data$Condition ,col.name = 'Condition')
  Idents(Participant.integrated.1) <- 'Condition'
  table(Idents(Participant.integrated.1))
  save(Participant.integrated.1,file = paste(file_dir,"/rep",repl," sim.RData",sep = ""))

  #Participant.integrated.1 <- RunPCA(Participant.integrated.1, features = Signal[[repl]], verbose = F)
  #p_DimPlot[[repl]] <- DimPlot(Participant.integrated.1, reduction = "pca",label.size = 1)

  # gene set size from 10 to 500
  noise <- c(0,0.2,0.5,0.8,1)
  GS_size <- c(10,20,30,40,50,100,200,300,400,500)
  up_sim<- list()
  for (i in 1:length(noise)){
    up_sim[[i]] <- paste("GS",c(rep(GS_size,each=100)),noise[i],1:100,sep = "_")
  }
  # create the gold-stander genesets
  gs<- list()
  set.seed(42)
  for (i in 1:10){
    N= GS_size[i]
    for (sim in 1:100){
      if (length(Signal[[repl]]) >= N){
        gs[[up_sim[[1]][sim+100*(i-1)]]] <- c(sample(Signal[[repl]],size = N,replace = F))
      } else{
        gs[[up_sim[[1]][sim+100*(i-1)]]] <- 0
      }
    }
  }
  # create genesets with noise
  set.seed(42)
  for (i in 2:length(noise)){
    for (j in 1:10){
      N= GS_size[j]
      for (sim in 1:100){
        if (length(Signal[[repl]]) >= (N-N*noise[i])){
          gs[[up_sim[[i]][sim+100*(j-1)]]] <- c(sample(Signal[[repl]],size = N*round((1-noise[i]),1),replace = F),sample(NonSignal[[repl]],size = N*noise[i],replace = F))
        }
        else{
          gs[[up_sim[[i]][sim+100*(j-1)]]] <- 0
        }
      }
    }
  }
  # make geneset.gmt file
  file = paste(file_dir,"/rep",repl," GS.gmt",sep = "")
  write.gmt <- function(gs,file){
    sink(file)
    lapply(names(gs),function(i){
      cat(paste(c(i,'tmp',gs[[i]]),collapse = '\t'))
      cat('\n')
    })
    sink()
  }
  write.gmt(gs,file)
}

# save
# saveRDS(rows_zeros.signal,file = "Scenario2_rows_zeros.signal.RWSD.rds")
# saveRDS(rows_zeros.nonsignal,file = "Scenario2_rows_zeros.nonsignal.RWSD.rds")
```

######## Uneuqual number of genes per condition  ##########
Scenario 3: 
Select densely expressed genes as for GS genes, and no signal was assigned to these genes in condition 2
Add 250 new genes (densly expressed genes) in condition 2 only and keep condition 1 == 0
Sample size 200 and GS size 10-500
```{r real Scenario 3}
setwd(File_dir)
File_dir
Scenario_set = "Scenario 3 scimpute"
dir.create(Scenario_set)
file_dir = paste0(File_dir,"/",Scenario_set)
Genes <- list()
Signal <- list()
NonSignal <- list()
Undetect <- list()

for (repl in 1:10){
  B_cell_subset <- Normal_Bcell[,colnames(Normal_Bcell)[sim.mc[,repl]]]
  B_cell_subset_meta_data <- data.frame(Condition=c(rep("Condition_1",cellcounts),rep("Condition_2",cellcounts))) # add condition meta
  rownames(B_cell_subset_meta_data) <- rownames(B_cell_subset@meta.data)
  B_cell_subset <- AddMetaData(B_cell_subset,metadata = B_cell_subset_meta_data)
  Idents(B_cell_subset) <- 'Condition'
  table(Idents(B_cell_subset))
  
  ## ----Gene signature simulation--------------------------------------------------
  rows_zeros = rowMeans(B_cell_subset@assays$RNA@data ==0)
  # Scenario 1 select genes detected in at least one cell
  Genes[[repl]] <- rownames(B_cell_subset@assays$RNA@data[rows_zeros < 1,])
  print(paste("Detected gene count",length(Genes[[repl]])))
  Undetect[[repl]] <- rownames(B_cell_subset@assays$RNA@data[rows_zeros == 1,])
  print(paste("Undetect gene count",length(Undetect[[repl]])))
  
  # Assign signal
  Signal[[repl]] <- rownames(B_cell_subset@assays$RNA@data[rows_zeros < Threshold,])
  print(paste("Signal gene count",length(Signal[[repl]])))
  NonSignal[[repl]] <- Genes[[repl]][-which(Genes[[repl]] %in% Signal[[repl]]) ]
  print(paste("Non singal gene count",length(NonSignal[[repl]])))
  dat <- as.matrix(B_cell_subset@assays$RNA@data)
  dat <- dat[rownames(dat) %in% Genes[[repl]],]
  dat[Signal[[repl]], which(B_cell_subset@meta.data$Condition %in% "Condition_2")] <- dat[Signal[[repl]], which(B_cell_subset@meta.data$Condition %in% "Condition_2")] * Signal_Level
  print(dim(dat))
  
  B_cell_subset <- Normal_Bcell[,colnames(Normal_Bcell)[sim.mc[,repl+1]]]
  B_cell_subset_meta_data <- data.frame(Condition=c(rep("Condition_1",cellcounts),rep("Condition_2",cellcounts))) # add condition meta
  rownames(B_cell_subset_meta_data) <- rownames(B_cell_subset@meta.data)
  B_cell_subset <- AddMetaData(B_cell_subset,metadata = B_cell_subset_meta_data)
  rows_zeros = rowMeans(B_cell_subset@assays$RNA@data ==0)
  Add_gene <- sample(rownames(B_cell_subset@assays$RNA@data[rows_zeros < Threshold,]),250,replace = F)
  print(paste("add gene count",length(Add_gene)))
  dat.1 <- as.matrix(B_cell_subset@assays$RNA@data)
  dat.1 <- dat.1[rownames(dat.1) %in% Add_gene,]
  print(dim(dat.1))
  dat.1[,which(B_cell_subset@meta.data$Condition %in% "Condition_1")] <- 0
  rownames(dat.1) <- paste0(Add_gene,"add")
  dat <- rbind(dat,dat.1)
  print(dim(dat))
  NonSignal[[repl]] <- c(NonSignal[[repl]],paste0(Add_gene,"add"))
  print(paste("Non singal gene count (+newly add genes)",length(NonSignal[[repl]])))
  
  # Create Seurat Object
  Participant.integrated.1 <- CreateSeuratObject(counts = dat)
  Participant.integrated.1 <- ScaleData(Participant.integrated.1,verbose = F)
  # Add condition meta
  Participant.integrated.1 <- AddMetaData(Participant.integrated.1,metadata = B_cell_subset@meta.data$Condition ,col.name = 'Condition')
  save(Participant.integrated.1,file = paste(file_dir,"/rep",repl," sim.RData",sep = ""))
  
  # gene set size from 10 to 500
  noise <- c(0,0.2,0.5,0.8,1)
  GS_size <- c(10,20,30,40,50,100,200,300,400,500)
  up_sim<- list()
  for (i in 1:length(noise)){
    up_sim[[i]] <- paste("GS",c(rep(GS_size,each=100)),noise[i],1:100,sep = "_")
  }
  # create the gold-stander genesets
  gs<- list()
  set.seed(42)
  for (i in 1:10){
    N= GS_size[i]
    for (sim in 1:100){
      if (length(Signal[[repl]]) >= N){
        gs[[up_sim[[1]][sim+100*(i-1)]]] <- c(sample(Signal[[repl]],size = N,replace = F))
      } else{
        gs[[up_sim[[1]][sim+100*(i-1)]]] <- 0
      }
    }
  }
  # create genesets with noise
  set.seed(42)
  for (i in 2:length(noise)){
    for (j in 1:10){
      N= GS_size[j]
      for (sim in 1:100){
        if (length(Signal[[repl]]) >= (N-N*noise[i])){
          gs[[up_sim[[i]][sim+100*(j-1)]]] <- c(sample(Signal[[repl]],size = N*round((1-noise[i]),1),replace = F),sample(NonSignal[[repl]],size = N*noise[i],replace = F))
        }
        else{
          gs[[up_sim[[i]][sim+100*(j-1)]]] <- 0
        }
      }
    }
  }
  # make geneset.gmt file
  file = paste(file_dir,"/rep",repl," GS.gmt",sep = "")
  write.gmt <- function(gs,file){
    sink(file)
    lapply(names(gs),function(i){
      cat(paste(c(i,'tmp',gs[[i]]),collapse = '\t'))
      cat('\n')
    })
    sink()
  }
  write.gmt(gs,file)
}
```

Scenario 4: 
Randomly selected gene as for GS genes, and no signal was assigned to these genes in condition 2
Add 250 new genes (randomly selecet 250 expressed genes) in condition 2 only and keep condition 1 == 0
Sample size 200 and GS size 10-500
```{r real Scenario 4}
setwd(File_dir)
File_dir
Scenario_set = "Scenario 4 scimpute"
dir.create(Scenario_set)
file_dir = paste0(File_dir,"/",Scenario_set)
Genes <- list()
Signal <- list()
NonSignal <- list()
Undetect <- list()

for (repl in 1:10){
  B_cell_subset <- Normal_Bcell[,colnames(Normal_Bcell)[sim.mc[,repl]]]
  B_cell_subset_meta_data <- data.frame(Condition=c(rep("Condition_1",cellcounts),rep("Condition_2",cellcounts))) # add condition meta
  rownames(B_cell_subset_meta_data) <- rownames(B_cell_subset@meta.data)
  B_cell_subset <- AddMetaData(B_cell_subset,metadata = B_cell_subset_meta_data)
  Idents(B_cell_subset) <- 'Condition'
  table(Idents(B_cell_subset))
  
  ## ----Gene signature simulation--------------------------------------------------
  rows_zeros = rowMeans(B_cell_subset@assays$RNA@data ==0)
  # Scenario 1 select genes detected in at least one cell
  Genes[[repl]] <- rownames(B_cell_subset@assays$RNA@data[rows_zeros < 1,])
  print(paste("Detected gene count",length(Genes[[repl]])))
  Undetect[[repl]] <- rownames(B_cell_subset@assays$RNA@data[rows_zeros == 1,])
  print(paste("Undetect gene count",length(Undetect[[repl]])))
  
  # Assign signal
  Signal[[repl]] <- sample(rownames(B_cell_subset@assays$RNA@data[rows_zeros < 1,]),550)
  print(paste("Signal gene count",length(Signal[[repl]])))
  NonSignal[[repl]] <- Genes[[repl]][-which(Genes[[repl]] %in% Signal[[repl]]) ]
  print(paste("Non singal gene count",length(NonSignal[[repl]])))
  dat <- as.matrix(B_cell_subset@assays$RNA@data)
  dat <- dat[rownames(dat) %in% Genes[[repl]],]
  dat[Signal[[repl]], which(B_cell_subset@meta.data$Condition %in% "Condition_2")] <- dat[Signal[[repl]], which(B_cell_subset@meta.data$Condition %in% "Condition_2")] * Signal_Level
  print(dim(dat))
  
  B_cell_subset <- Normal_Bcell[,colnames(Normal_Bcell)[sim.mc[,repl+1]]]
  B_cell_subset_meta_data <- data.frame(Condition=c(rep("Condition_1",cellcounts),rep("Condition_2",cellcounts))) # add condition meta
  rownames(B_cell_subset_meta_data) <- rownames(B_cell_subset@meta.data)
  B_cell_subset <- AddMetaData(B_cell_subset,metadata = B_cell_subset_meta_data)
  rows_zeros = rowMeans(B_cell_subset@assays$RNA@data ==0)
  Add_gene <- sample(rownames(B_cell_subset@assays$RNA@data[rows_zeros < 1,]),250,replace = F)
  print(paste("add gene count",length(Add_gene)))
  dat.1 <- as.matrix(B_cell_subset@assays$RNA@data)
  dat.1 <- dat.1[rownames(dat.1) %in% Add_gene,]
  print(dim(dat.1))
  dat.1[,which(B_cell_subset@meta.data$Condition %in% "Condition_1")] <- 0
  rownames(dat.1) <- paste0(Add_gene,"add")
  dat <- rbind(dat,dat.1)
  print(dim(dat))
  NonSignal[[repl]] <- c(NonSignal[[repl]],paste0(Add_gene,"add"))
  print(paste("Non singal gene count (+newly add genes)",length(NonSignal[[repl]])))
  
  # Create Seurat Object
  Participant.integrated.1 <- CreateSeuratObject(counts = dat)
  Participant.integrated.1 <- ScaleData(Participant.integrated.1,verbose = F)
  # Add condition meta
  Participant.integrated.1 <- AddMetaData(Participant.integrated.1,metadata = B_cell_subset@meta.data$Condition ,col.name = 'Condition')
  save(Participant.integrated.1,file = paste(file_dir,"/rep",repl," sim.RData",sep = ""))
  
  # gene set size from 10 to 500
  noise <- c(0,0.2,0.5,0.8,1)
  GS_size <- c(10,20,30,40,50,100,200,300,400,500)
  up_sim<- list()
  for (i in 1:length(noise)){
    up_sim[[i]] <- paste("GS",c(rep(GS_size,each=100)),noise[i],1:100,sep = "_")
  }
  # create the gold-stander genesets
  gs<- list()
  set.seed(42)
  for (i in 1:10){
    N= GS_size[i]
    for (sim in 1:100){
      if (length(Signal[[repl]]) >= N){
        gs[[up_sim[[1]][sim+100*(i-1)]]] <- c(sample(Signal[[repl]],size = N,replace = F))
      } else{
        gs[[up_sim[[1]][sim+100*(i-1)]]] <- 0
      }
    }
  }
  # create genesets with noise
  set.seed(42)
  for (i in 2:length(noise)){
    for (j in 1:10){
      N= GS_size[j]
      for (sim in 1:100){
        if (length(Signal[[repl]]) >= (N-N*noise[i])){
          gs[[up_sim[[i]][sim+100*(j-1)]]] <- c(sample(Signal[[repl]],size = N*round((1-noise[i]),1),replace = F),sample(NonSignal[[repl]],size = N*noise[i],replace = F))
        }
        else{
          gs[[up_sim[[i]][sim+100*(j-1)]]] <- 0
        }
      }
    }
  }
  # make geneset.gmt file
  file = paste(file_dir,"/rep",repl," GS.gmt",sep = "")
  write.gmt <- function(gs,file){
    sink(file)
    lapply(names(gs),function(i){
      cat(paste(c(i,'tmp',gs[[i]]),collapse = '\t'))
      cat('\n')
    })
    sink()
  }
  write.gmt(gs,file)
}
```

